True Stellar Obliquity Distribution of Exoplanets

### 2022-11-15 src/tex/ms.tex
[showyourwork] overleaf sync

% Abstract with filler text
\begin{abstract}
We build a hierarchical Bayesian framework to constrain exoplanets' true stellar obliquity ($\psi$) distribution. Using the sky-projected stellar obliquities ($\lambda$)  of a sample of 162 exoplanets, we infer their $\cos{\psi}$ distribution using a four-parameter Beta mixture model under the assumption of a uniform cosine of the stellar inclination ($\cos{i_\star}$) bounded between $-1$ and $1$. We find a significant pile-up of $\cos{\psi}$ near 1, suggesting that the majority of exoplanetary systems are well aligned. For misaligned systems, we find $\cos{\psi}$ is uniformly distributed between $-0.75$ to $0.5$ and have a slight but insignificant preference to $\cos{\psi} = -0.25$, corresponding to $\psi = 104.5\degr$. A pile-up at $\cos{\psi} = 0$ is not found.
\end{abstract}

>>>>

% Abstract with filler text
\begin{abstract}
We build a hierarchical Bayesian framework to constrain exoplanets' true stellar obliquity ($\psi$) distribution. Using the sky-projected stellar obliquities ($\lambda$)  of a sample of 162 exoplanets, we infer their $\cos{\psi}$ distribution using a four-parameter Beta mixture model with the assumption of a uniform cosine of stellar inclination ($\cos{i_\star}$) distribution for each planet. We find a significant pile-up of $\cos{\psi}$ near 1, suggesting that the majority of exoplanetary systems are well aligned. For misaligned systems, we find $\cos{\psi}$ is uniformly distributed between $-0.75$ to $0.5$ with no significant pipe-up near $\cos{\psi} = 0$.
\end{abstract}
